Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-24 PaperBCJ.tex
Fix spaces

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication} , providing new means to approach problems in a different manner. The availability of leading edge technologies has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products\cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. 
\\

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

>>>>

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication}, providing new means to approach problems in a different manner. The availability of leading edge technologies has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products\cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. 
\\

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching \cite{ortiz2012máquinas}. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\
